Vulnerability Analysis of Container Images in Neuroimaging

### 2020-07-17 paper.tex
content fix 2

\renewcommand{\labelitemi}{$\textendash$}
\title{Vulnerability Analysis of Container Images in Neuroimaging}
\begin{filecontents*}{resul.csv}
labels,names,A,C,V,Stools
a,bids/example:latest,838,663,683,
b,bids/freesurfer:latest,353,215,192,
c,bids/ndmg:latest,934,757,782,
d,\textbf{bids/broccoli:v1.0.0},79,79,117,
e,bids/fibredensityandcrosssection:latest,1086,849,868,
f,bids/spm:latest,191,246,235,
g,poldracklab/mriqc:0.15.0,432,328,332,
h,bids/cpac:v1.0.1a\_22,698,524,535,
I,bids/hyperalignment:latest,1717,1327,1433,
j,bids/mindboggle:0.0.4-1,671,955,569,
k,bids/mrtrix3\_connectome:latest,275,157,158,
l,bids/rs\_signal\_extract:0.1,867,454,473,
m,bids/aa:v0.2.0,189,244,233,
n,bids/niak:latest,1482,1366,1420,
o,bids/oppni:v0.7.0-1,913,698,723,
p,poldracklab/fmriprep:unstable,516,355,393,
q,bids/brainiak-srm:latest,897,484,503,
r,bids/nipypelines:0.3.0,641,878,451,
s,bids/hcppipelines:v3.17.0-18,526,873,620,
t,bids/magetbrain:latest,112,117,126,
u,bids/tracula:v6.0.0-4,874,664,683,
v,bids/baracus:latest,172,238,216,
w,bids/antscorticalthickness:v2.2.0-1,289,27,no OVAL data,
x,bids/dparsf:v4.3.12,507,750,757,
y,bids/afni\_proc:latest,67,16,no OVAL data,
z,bids/rshrf:1.0.1,5,3,3,
aa,bids/ndmg:v0.1.0,934,758,782,
ab,\textbf{mcin/qeeg:latest},46,46,142,
ac,\textbf{camarasu/creaphase:0.3},54,54,186,
ad,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest},70,76,157,
ae,\textbf{mcin/docker-fsl:latest},75,75,201,
af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
ag,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest},70,76,157,
ah,\textbf{bt5e/ants:latest},150,156,336,
ai,poldracklab/fmriprep:1.2.3,591,441,447,
aj,gkiar/dwipreproc\_fsl-5.0.11\_minified:latest,391,258,263,
ak,gkiar/mask2boundary:v0.1.0,15,11,11,
al,\textbf{mcin/ica-aroma:latest},75,75,202,
am,c3genomics/genpipes,,,,99
an,bioinformatics-group/aqua-singularity-recipe,,,,7
ao,MontrealSergiy/BEst,,,,106
ap,shub://aces/cbrain-containers-recipes:fsl\_v6.0.1,,,,206
aq,shots47s/bids-freesurfer-6.0,,,,212
ar,shots47s/bids-fmriprep-1.2.3,,,,453
\end{filecontents*}

@@

\begin{figure*}
\begin{tabular}{ |c|c|c|c| }
 \hline
\textbf{OS} &	\textbf{Anchore} &	\textbf{Vuls} &	\textbf{Clair} \\
\hline
	\textbf{Alpine} & Alpine-SecDB &	Alpine-SecDB &	Alpine-SecDB \\
\hline
	\textbf{CentOS} & Red Hat Enterprise Linux Oval & Red Hat Enterprise Linux OVAL And Red Hat Security Advisories & Red Hat Security Data \\
\hline
	\textbf{Debian} & Debian Security Bug Tracker &	Debian OVAL and Debian Security Bug Tracker & Debian Security Bug Tracker \\
\hline
	\textbf{Ubuntu} & Ubuntu CVE Tracker &	Ubuntu OVAL &	Ubuntu CVE Tracker \\
 \hline
\end{tabular}
\caption{Vulnerability databases used by scanners for different OS distributions}
\label{database}
\end{figure*}

@@

\subsection{Ubuntu Releases and its Vulnerability Database}

BIDS apps and Boutiques images in our experiments have four Linux
distributions i.e. Ubuntu, CentOS, Debian, and Alpine. A particular
distribution has different releases in general. Regarding Ubuntu, it has different
types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
Through our experiments, we find that image scanners report Ubuntu vulnerabilities 
differently depending on the different Ubuntu release types. It is 
important to provide an overview of these Ubuntu releases types, 
since Ubuntu is heavily utilized in our experiments. 
Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of ESM release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
to LTS release only while collecting data from the vulnerability databases.
More interestingly, scanners are able to refer to ESM release vulnerability database
even without purchase, however, this may lead to discrepancies in results.
Further, if an image is using a Linux release where EOL has been reached that image may
turns to be vulnerable as it is not possible to retrieve any updates.

Ubuntu maintains its vulnerability database in the Ubuntu CVE Tracker. For a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
For a given release, the status can be any one of the following:

@@

\textbf{not-affected:} The package, while related to the
		CVE in some way, is not affected by the issue. Notes should
		provide detailed information, if needed. For instance, if the given
		status is "not-affected (1.14.6-1.1)" then this indicates that this specific
		package version is not affected.

@@

Figure~\ref{example} illustrates how the information of a CVE is represented
in the Ubuntu launchpad database.

\begin{figure}[!ht]
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
\end{figure}
\vspace*{-7mm}
\section{Reducing the amount of vulnerabilities}

@@

Table~\ref{table1} shows the number of detected vulnerabilities in the different images,
detected by each of the scanners. Image labels from \texttt{a} to \texttt{al} represents
Docker images, whereas remaining ones belong to Singularity.
Vuls shows \textit{no OVAL data} for image \texttt{w} and \texttt{y},
which have Ubuntu 17.04 and 17.10 OS distribution respectively. This is because there is no
vulnerability data present in OVAL database, which Vuls refers for Ubuntu distributions, for these two releases.

Figure~\ref{fig:graph1} provides more image-specific information.
It represents the number of vulnerabilities that are present inside each images.
The overall trend shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The Figure also infers that the Alpine distribution, being a
lightweight distribution, has the least number of vulnerabilities, whereas more vulnerabilities are reported for
distributions with more packages such as Ubuntu.
We also analyze that out of the total Docker images scanned by our experiments, Debian reports more high vulnerabilties, as
classified by databases, than others.
\begin{table*}[!ht]
\csvreader[%
 tabular={|c|c|c|c|c|c|},
	table head = \hline\textbf{Image Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
	late after line= \\,
        late after last line=\\\hline %
	]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
        {\labels & \names & \A & \C & \V & \Stools}
       \centering
	\vspace*{1mm}
	\caption{\label{table1}Number of vulnerabilities by scanners (all Centos images are highlighted)} 
\end{table*}

\begin{figure*}[!ht]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/vulngraph.pdf}}
	\vspace*{-7mm}
        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
      \end{figure*}

\begin{figure}[!ht]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/venn.pdf}}
	\vspace*{-10mm}
	\caption{\label{fig:venn} Scanner results (excluding non-comparable image results)}
\end{figure}

@@

Our experiments concluded considerable discrepancies in the results obtained by
these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
While comparing scanner results, we exluded all Centos images (highlighted images in Table~\ref{table1})
and two other images \texttt{w} and
\texttt{y}. The reason behind excluding Centos images is that scanners report results using different
vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
to report pending patches that need to be applied to specific packages,
whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
vulnerabilities in packages. We exluded \texttt{w} and \texttt{y} images because Vuls
can not scan these image, hence no results to compare.
In most cases,
Anchore reports more vulnerabilities than Vuls and Clair resulting in 
the Jaccard coefficient of 0.59 with both,
whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.83.
Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners in Docker images and the overlap between them.
This Figure also excludes Centos Docker images and \texttt{w} and \texttt{y} images.
It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 by Clair, and 325 by Vuls.

@@

\textbf{Linux-kernel-headers:} Clair and Vuls are ignore all vulnerabilities in the Linux-kernel-headers,
whereas Anchore reports all of them.
We find that 4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
detected by both Vuls and Clair.
Linux-kernel-headers are the headers files that only provide function names, their parameters, and their
return types.
The actual source code of these functions is present in the Linux kernel and is not inside the image.
So, vulnerability detection in header files
is irrelevant in this case.

\textbf{CVEs with Status as “Not-affected”:} Vuls reports vulnerabilities that have status
as "not-affected" in the vulnerability database. It means the Linux distribution of the image is not affected
by the particular CVE. In other words, Vuls reports vulnerabilities that it should not have been reported.
For example, we scan an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, upon checking the vulnerability database, we find that package Cups in Trusty is not
affected by this CVE.

\textbf{CVEs with status as "Ignored (reached end-of-life)":}
Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release, these vulnerabilities may or may not be present.
Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
If this kind of vulnerability is present in ESM release then Clair reports it because it
only refers to ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE" (Does Not Exist), then Clair does not report it. 
For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to end-of-life.
Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
release so Clair also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
Clair still refers to Ubuntu 14.04 ESM release vulnerability database, which is incorrect.

@@

\begin{figure*}[!ht]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
	\vspace*{-5mm}
        \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
      \end{figure*}
\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair but they affect Ubuntu 14.04 LTS, and hence detected by Vuls. The CVE-2017-1375 is an example
of such vulnerabilities.

@@

\textbf{Database difference:} At the time we pulled Clair's database image, it was one week old.
                              As a result some vulnerabilities were not updated. For instance, CVE-2019-5094, which
		              was published on 2019-09-24, was not 
		              updated in Clair's database. Due to which it is missed by Clair.
			      Consequently, these discrepancies, even small, are sufficient to change the detection of
			      the scanners.

@@

\textbf{CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair. 
		For instance, CVE-2019-13565, which is present in Ubuntu 14.04, is an example of such vulnerabilities. 
		We reported this bug as well to the Anchore development team through their Slack
		channel.

\textbf{Rejected CVEs:} There are some CVEs, such as CVE-2017-13753, that are rejected because they are duplicate copies of other CVEs. 
	So, Anchore does not report those rejected CVEs, but Vuls reports them.

@@

As a result of image updating,
scanning results change significantly.
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
image update. 
In fact, this Figure combines the original results of Figure~\ref{fig:graph1} with the results of the image update
experiment.
Clearly, the figure illustrates that when image are updated, the number of vulnerabilities reduces by a
significant number. Furthermore, a mild slope of vulnerabilities after the image update shows that
there is a set of packages that contain vulnerabilities and have not been fixed yet. Also, these
vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status, meaning that
high vulnerabilities are prioritised and fixed fast.
Besides that, it is also interesting to note that some images in Figure~\ref{fig:graph2}
do not have update results. This is because some Linux distributions reached end-of-life and
are not being updated anymore.
Despite of the significant drop in the number of vulnerabilities as a result of image updating,
there is still a number of vulnerabilities reported by the scanners. There is due to the
vulnerabilities which do not have fix yet.

@@

Our second approach involves the deletion of unnecessary packages from the images.
We tested our approach on 5 different images. We find that
after the size reduction process, sometimes the scanning results deviate only a little from the results
without minimization. While the minimization process results in significant reduction
in the number of vulnerabilities in some cases, we find that in other cases the effect
is negligible. In other words, the image reduction was inconsistent.
According to our analysis, this can be due to two reasons: \rom{1}) the number of
deleted packages
and \rom{2}) the kind of deleted packages. 
For an instance, if the deletion is for a package that includes a lot of vulnerabilities,
that particular deletion naturally results in the drop of number of vulnerabilities.
In other
words, deleting more packages reduces more vulnerabilities. 
For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.

@@

Our last experiment includes updating the image and then removing unnecessary packages from it.
Figure~\ref{fig:bargraph} displays the results. 
Our initial thought was that with the update and size reduction process together, we will be able to
reduce vulnerabilities even more. However,
we analyzed that this is not always true. Again, it depends on which packages are deleted and how
many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments 2 and 4.
Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
scanning results did not change.
\vspace*{-2mm}
\section{Discussion}

>>>>

\renewcommand{\labelitemi}{$\textendash$}
\title{Vulnerability Analysis of Container Images in Neuroimaging}
\begin{filecontents*}{resul.csv}
labels,names,A,C,V,Stools
a,bids/example:latest,838,663,683,
b,bids/freesurfer:latest,353,215,192,
c,bids/ndmg:latest,934,757,782,
d,\textbf{bids/broccoli:v1.0.0},79,79,117,
e,bids/fibredensityandcrosssection:latest,1086,849,868,
f,bids/spm:latest,191,246,235,
g,poldracklab/mriqc:0.15.0,432,328,332,
h,bids/cpac:v1.0.1a\_22,698,524,535,
I,bids/hyperalignment:latest,1717,1327,1433,
j,bids/mindboggle:0.0.4-1,671,955,569,
k,bids/mrtrix3\_connectome:latest,275,157,158,
l,bids/rs\_signal\_extract:0.1,867,454,473,
m,bids/aa:v0.2.0,189,244,233,
n,bids/niak:latest,1482,1366,1420,
o,bids/oppni:v0.7.0-1,913,698,723,
p,poldracklab/fmriprep:unstable,516,355,393,
q,bids/brainiak-srm:latest,897,484,503,
r,bids/nipypelines:0.3.0,641,878,451,
s,bids/hcppipelines:v3.17.0-18,526,873,620,
t,bids/magetbrain:latest,112,117,126,
u,bids/tracula:v6.0.0-4,874,664,683,
v,bids/baracus:latest,172,238,216,
w,bids/antscorticalthickness:v2.2.0-1,289,27,no data,
x,bids/dparsf:v4.3.12,507,750,757,
y,bids/afni\_proc:latest,67,16,no data,
z,bids/rshrf:1.0.1,5,3,3,
aa,bids/ndmg:v0.1.0,934,758,782,
ab,\textbf{mcin/qeeg:latest},46,46,142,
ac,\textbf{camarasu/creaphase:0.3},54,54,186,
ad,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest},70,76,157,
ae,\textbf{mcin/docker-fsl:latest},75,75,201,
af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
ag,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest},70,76,157,
ah,\textbf{bt5e/ants:latest},150,156,336,
ai,poldracklab/fmriprep:1.2.3,591,441,447,
aj,gkiar/dwipreproc\_fsl-5.0.11\_minified:latest,391,258,263,
ak,gkiar/mask2boundary:v0.1.0,15,11,11,
al,\textbf{mcin/ica-aroma:latest},75,75,202,
am,c3genomics/genpipes,,,,99
an,bioinformatics-group/aqua-singularity-recipe,,,,7
ao,MontrealSergiy/BEst,,,,106
ap,shub://aces/cbrain-containers-recipes:fsl\_v6.0.1,,,,206
aq,shots47s/bids-freesurfer-6.0,,,,212
ar,shots47s/bids-fmriprep-1.2.3,,,,453
\end{filecontents*}

@@

\begin{figure*}
\begin{tabular}{|c|c|c|c|}
 \hline
\textbf{OS} &	\textbf{Anchore} &	\textbf{Vuls} &	\textbf{Clair} \\
\hline
	\textbf{Alpine} & Alpine-SecDB &	Alpine-SecDB &	Alpine-SecDB \\
\hline
	\textbf{CentOS} & Red Hat OVAL Database & Red Hat OVAL Database and Red Hat Security Advisories & Red Hat Security Data \\
\hline
	\textbf{Debian} & Debian Security Bug Tracker &	Debian OVAL Database and Debian Security Bug Tracker & Debian Security Bug Tracker \\
\hline
	\textbf{Ubuntu} & Ubuntu CVE Tracker &	Ubuntu OVAL Database &	Ubuntu CVE Tracker \\
 \hline
\end{tabular}
\caption{Vulnerability databases used by scanners for different OS distributions}
\label{database}
\end{figure*}

@@

\subsection{Ubuntu Release types and its Vulnerability statuses}

BIDS apps and Boutiques images in our experiments have four Linux
distributions i.e. Ubuntu, CentOS, Debian, and Alpine. 
Out of these distributions, Ubuntu assigns a vulnerability status to
all vulnerabilities before keeping them in its vulnerability database.
Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
Ubuntu keeps a record of Ubuntu-specific vulnerabilities in Ubuntu CVE Tracker using their CVE
numbers. In this paper, we use vulnerability and CVE interchangeably.
The vulnerability status in Ubuntu CVE Tracker is subjected to change
depending on the work progress to fix that vulnerability.
%Regarding Ubuntu, it has different
%types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
%Ubuntu maintains its vulnerability data in Ubuntu CVE tracker, which is referred by Anchore and Clair.
%There is another vulnerability database i.e. Open Vulnerability and Assessment Language (OVAL) repository,
%which is maintained by MITRE corporation. Vuls refers to OVAL repository for getting Ubuntu vulnerability feed.
%The vulnerability data format of both databases is different. OVAL keeps a separate xml file for each release,
%which contains that release specific vulnerability information.
Ubuntu keeps a separate file for each vulnerability, which
has an entry for all Ubuntu releases combined with the current status
of that vulnerability in that release.
Further, in Ubuntu a particular release can be of different types i.e. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release. 
Through our experiments, we find that Anchore and Clair report Ubuntu vulnerabilities 
differently depending on either the different Ubuntu release type or vulnerability status. It is 
important to provide an overview of these Ubuntu releases types and vulnerability statuses, 
since Ubuntu is heavily utilized in our experiments. 
Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of ESM release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
to LTS release only while collecting data from the vulnerability databases.
More interestingly, Clair refers to ESM release vulnerability database, however, this may lead to discrepancies in results.
Further, if an image is using a Linux release where EOL has been reached that image may
turns to be vulnerable as it is not possible to retrieve any updates.

In Ubuntu CVE Tracker, all Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a vulnerability status
(\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
For a given release, the vulnerability status can be any one of the following:

@@

\textbf{not-affected:} The package, while related to the
		CVE in some way, is not affected by the issue. The <notes> should
		provide detailed information, if needed. For instance, if the given
		status is "not-affected (1.14.6-1.1)" then this indicates that this specific
		package version is not affected.

@@

Figure~\ref{example} illustrates how the information of a CVE is represented
in the Ubuntu CVE Tracker.

\begin{figure}[!ht]
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu CVE Tracker}
\end{figure}
\vspace*{-7mm}
\section{Reducing the amount of vulnerabilities}

@@

Table~\ref{table1} shows the number of vulnerabilities in the different images,
detected by each of the scanners. Image labels from a to al represents
Docker images, whereas remaining ones belong to Singularity.
Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest},
which have Ubuntu 17.04 and 17.10 OS distribution respectively. This is because there is no
vulnerability data present in OVAL database, which Vuls refers for Ubuntu distributions, for these two releases.

Figure~\ref{fig:graph1} provides more image-specific information.
It represents the number of vulnerabilities that are present inside each images.
The overall trend shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
This Figure also infers that the Alpine distribution, being a
lightweight distribution, has the least number of vulnerabilities, whereas more vulnerabilities are reported for
distributions with more packages such as Ubuntu.
We also analyze that out of the total Docker images scanned by our experiments, Debian reports more high-level vulnerabilties, as
classified by databases, than others.
\begin{table*}
\csvreader[%
 tabular={|c|c|c|c|c|c|},
	table head = \hline\textbf{Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
	late after line= \\,
        late after last line=\\\hline %
	]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
        {\labels & \names & \A & \C & \V & \Stools}
       \centering
	\vspace*{1mm}
	\caption{\label{table1}Number of vulnerabilities by scanners (all Centos images are highlighted)} 
\end{table*}

\begin{figure*}
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/vulngraph.pdf}}
	\vspace*{-7mm}
        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
      \end{figure*}

\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/venn.pdf}}
	\vspace*{-10mm}
	\caption{\label{fig:venn} Scanner results (excluding non-comparable image results)}
\end{figure}

@@

Our experiments concluded considerable discrepancies in the results obtained by
these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
While comparing scanner results, we exluded all Centos images (highlighted images in Table~\ref{table1})
and two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
\texttt{bids/antscorticalthickness:v2.2.0-1}. The reason behind excluding Centos images is that scanners report results using different
vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
to report pending patches that need to be applied to specific packages,
whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
vulnerabilities in packages. We exluded other two images because Vuls
can not scan these image, hence no results are present to compare.
In most cases,
Anchore reports more vulnerabilities than Vuls and Clair resulting in 
the Jaccard coefficient of 0.59 with both,
whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.83.
Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners in Docker images and the overlap between them.
This Figure also excludes Centos Docker images and other two non-comparable images.
It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 by Clair, and 325 by Vuls.

@@

\textbf{Linux-kernel-headers:} Clair and Vuls ignore all vulnerabilities in the Linux-kernel-headers,
whereas Anchore reports all of them.
We find that 4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
For example, CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, reported by Anchore, is not
detected by both Vuls and Clair.
Linux-kernel-headers are the header files that only provide function names, their parameters, and their
return types.
The actual source code of those functions is present in the Linux kernel and is not inside the image.
So, vulnerability detection in header files
is irrelevant in this case.

\textbf{Ubuntu CVEs with status as “Not-affected”:} Vuls reports vulnerabilities that have status
as "not-affected" in the Ubuntu database. It means that according to Ubuntu the image is not affected
by the particular vulnerability. In other words, Vuls reports vulnerabilities that it should not have been reported.
For example, when we scan an image having the Trusty release in it and Vuls reports CVE-2015-2305
in the package Cups. However, upon checking the Ubuntu vulnerability database, we find that package Cups in Trusty is not
affected by this CVE.

\textbf{Ubuntu CVEs with status as "Ignored (reached end-of-life)":}
Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release, these vulnerabilities may or may not be present.
Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
If this kind of vulnerability is present in ESM release then Clair reports it because it
only refers to ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE" (Does Not Exist), then Clair does not report it. 
For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to its end-of-life.
Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
release so Clair also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
Clair's referring to Ubuntu 14.04 ESM release vulnerability database is incorrect.

@@

\begin{figure*}[!ht]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
	\vspace*{-5mm}
        \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
      \end{figure*}
\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair but they affect Ubuntu 14.04 LTS, and hence detected by Vuls and Anchore. The CVE-2017-13758 is an example
of such vulnerabilities.

@@

\textbf{Database difference:} At the time we pulled Clair's database, through \texttt{arminc/clair-db:latest} Docker image, it was one week old.
                              As a result some vulnerabilities were not updated in the database. For instance, CVE-2019-5094, which
		              was published on 2019-09-24, was not 
		              updated in Clair's database. Due to which it is missed by Clair.
			      Consequently, these discrepancies, even small, are sufficient to change the detection of
			      the scanners.

@@

\textbf{Ubuntu CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair. 
		For instance, CVE-2019-13565, which is present in Ubuntu 14.04 LTS, is an example of such vulnerabilities. 
		We reported this bug as well to the Anchore development team through their Slack
		channel.

\textbf{Rejected CVEs:} There are some CVEs, such as CVE-2017-13753, that are rejected because they are duplicate copies of other CVEs. 
	So, Anchore and Clair does not report those rejected CVEs, but Vuls reports them.

@@

As a result of image updating,
scanning results change significantly.
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
image update. 
In fact, this Figure combines the original results of Figure~\ref{fig:graph1} with the results of the image update
experiment.
Clearly, the figure illustrates that when images are updated, the number of vulnerabilities reduces by a
significant number. Furthermore, a mild slope of vulnerabilities after the image update shows that
there is a set of packages that contain vulnerabilities and have not been fixed yet. Also, these
vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status, meaning that
\textit{high} severity vulnerabilities are prioritized and fixed fast.
Besides that, it is also interesting to note that some images in Figure~\ref{fig:graph2}
do not have update results. This is because some Linux distributions reached end-of-life and
are not being updated anymore.
Despite of the significant drop in the number of vulnerabilities as a result of image updating,
there is still a number of vulnerabilities reported by the scanners. This is due to the
vulnerabilities which do not have fix yet.

@@

Our second approach involves the deletion of unnecessary packages from the images.
We tested our approach on 5 different images covering the spectrum of Figure~\ref{fig:graph1}. We find that
after the size reduction process, sometimes the scanning results deviate only a little from the results
without minimization. While the minimization process results in significant reduction
in the number of vulnerabilities in some cases, we find that in other cases the effect
is negligible. In other words, the image reduction was inconsistent.
According to our analysis, this can be due to two reasons: \rom{1}) the number of
deleted packages
and \rom{2}) the kind of deleted packages. 
For an instance, if the deletion is for a package that includes a lot of vulnerabilities,
that particular deletion naturally results in the drop of number of vulnerabilities.
In other
words, deleting more packages reduces more vulnerabilities. 
For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.

@@

Our last experiment includes updating the image and then removing unnecessary packages from it.
Figure~\ref{fig:bargraph} displays the results. 
Our initial expectation was that with the update and size reduction process together, we will be able to
reduce vulnerabilities even more. However,
we analyzed that this is not always true. Again, it depends on which packages are deleted and how
many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments.
Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
scanning results did not change.
\vspace*{-2mm}
\section{Discussion}
